\chapter{Experiments}
\label{chap:experiments}

A suite of experiments performed on multiple robots
both in simulation and on actual hardware.
Scoped by the problem described in Chapter~\ref{chap:formulation}.

This chapter deals with whole-planner comparisons.
For evaluatoints of the individual algorithms in isolation,
see the associated chapters.
E.g. E$^8$, the E$^8$-PRM, the Multi-Set PRM, etc.

\section{Metrics}

Here are some metrics we propose to use:
\begin{itemize}
\item Full CDFs of *planning time*, *execution time*,
   and *total time* for each task
\item Success rate (within time budget)
\end{itemize}

Full CDFS of planning, execution, and total effort.

Time (s) and energy (J).

Success rates for different budgets.

\section{Control Variables}

Several things to control for to identify what parts of our framework
are most important for different types of structure.

Parameters/structure in my approach to vary to find out
what's important:
\begin{itemize}
\item The $\lambda$ parameter
\item The batching approach
\item What kinds of multi-set structure is exploited
\end{itemize}

Addressing fully known and fully unknown worlds.
Find out what really matters.

For example, I really want to talk about robots idly
hypothesizing worlds.

\section{Baseline Approaches}

\cdnote{Looking for suggestions for committee members here!}

DRC Trials approach

HPN (committing early, interleaved?)

Symbolic planners with symbolic stuff ripped out

Compare to anytime planners.

Compare to hybrid planners,
both interleaved and non-interleaved.

We compare against a few different task planners.

\begin{itemize}
\item The DRC Trials approach.
\item Some symbolic planners, with the symbolic stuff ripped out?
   Tak to Evan!
\item Hierarchical Planning in the Now (with however it commits things)
\end{itemize}

\section{Test Platforms}

We give a bunch of examples of this framework
for different robots.
HERB and CHIMP.
Simulation and real robots.


\section{Primary Comparison (No Interleaving)}

\subsection{DRC Experiments (Real Competition Data)}

\subsection{HERB Experiments}

\section{Secondary Comparison}

Allowing interleaved planning and execution
on deterministic, reversible worlds.
We expect planners like HPN to get a speedup
due to pipelining.

\section{Non-Reversable Problems}

What if actions cannot be undone?
