\documentclass{report}

\usepackage{standalone}

\usepackage[bookmarks=true]{hyperref}

% symbols
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb} % for \square

% from http://tex.stackexchange.com/a/5255
\DeclareMathOperator*{\argmin}{arg\,min}

% algorithm stuff
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage{array}
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,calc,patterns,positioning,shapes,decorations.pathmorphing}

% plots
\usepackage{pgfplots}

% pretty tables
\usepackage{multirow}
\usepackage{booktabs}

% custom title page
\usepackage{titling}

% for adjustwidth
\usepackage{changepage}

% simple paragraph stuff
\parindent=0pt
\parskip=6pt

% include \paragraph as numbered
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{2} % 3

%\def\hidenotes{}
% list of commenters
\newcommand{\ssnote}[1]{{\xxnote{SS}{red}{#1}}}
\newcommand{\cdnote}[1]{{\xxnote{CD}{blue}{#1}}}
\newcommand{\mknote}[1]{{\xxnote{MK}{green}{#1}}}
% implement conditional notes (turn on/off with \hidenotes above)
\newcommand{\xxnote}[3]{}
\ifx\hidenotes\undefined
  \usepackage{color}
  \renewcommand{\xxnote}[3]{\color{#2}{#1: #3}}
\fi

% wide page for side by side figures, tables, etc
% see http://tex.stackexchange.com/a/154766
\newlength{\offsetpage}
\setlength{\offsetpage}{1.5in}
\newenvironment{widepage}
   {\begin{adjustwidth}{-\offsetpage}{-\offsetpage}%
    \addtolength{\textwidth}{2\offsetpage}}%
{\end{adjustwidth}}

% theorems
\newtheorem{invariant}{Invariant}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
% from http://www.maths.tcd.ie/~dwilkins/LaTeXPrimer/Theorems.html
\newenvironment{proof}[1][Proof]{\begin{trivlist}
   \item[\hskip \labelsep {\bfseries #1}]}{\hfill$\square$\end{trivlist}}

\title{Efficient Manipulation Task Planning via\\
   Reuse-Informed Optimization of Planning Effort}
\author{Christopher M. Dellin}
\date{\today}

\renewcommand{\maketitlehookd}{
\begin{center}
\vspace{0.7in}
The Robotics Institute\\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\vspace{0.7in}
\textbf{Thesis Committee:}\\
Siddhartha Srinivasa, CMU RI (Chair)\\
Anthony Stentz, CMU RI\\
Maxim Likhachev, CMU RI\\
Lydia Kavraki, Rice University\\
%\vspace{0.7in}
%\emph{Submitted in partial fulfillment of the requirements\\
%for the degree of Doctor of Philosophy.}
\end{center}
}

\begin{document}

\maketitle

\begin{abstract}
\cdnote{This is still from the RSS paper.
The intro is more up-to-date.}
Motion planning approaches that build graphs
in the collision-free subset of configuration space
have proven promising
for high-dimensional articulated robotics problems
in unstructured environments.
However, many complex tasks (e.g. manipulation)
present two primary challenges.
First, the subset of collision-free configurations changes each time
the robot, objects, or people move, items are grasped or released,
or the fidelity of the robot's models changes.
This makes it difficult not only to apply the results of prior
planning computation to the current problem,
but also to efficiently consider planned or hypothesized motions,
especially in multi-step tasks.
Second, human-scale tasks are time-sensitive,
and these approaches incur significant planning cost
(comparable to execution cost)
which is dominated by collision checking.
To address these challenges,
we make two principal contributions.
First, we introduce \emph{multi-set planning},
a formulation which explicitly represents structure
between similar problems in C-space
using set-theoretic relations
and a cost model incorporating both planning and execution costs.
Second, we present the \emph{Multi-Set PRM} algorithm
which exploits this representation
by applying best-first search over roadmaps
with an objective which optimistically minimizes these costs.
We show that this approach automatically reuses planning computation
from similar problems when useful,
naturally replicating diverse behavior from prior
manipulation work designed to improve planner efficiency,
such as cached graphs, conservative bounding volumes,
and handling of dynamic environments.
We detail experimental results on a multi-step
manipulation task which show greater than a 3x improvement
in planning costs,
and provide an open-source implementation of our planner.
\end{abstract}

\tableofcontents

\include{ch01-intro}
\include{ch02-subprobs}
\include{ch03-e8}
\include{ch04-continuous}
\include{ch05-multiset}
\include{ch06-multisetprm}
\include{ch07-cmr}
\include{ch08-taskplanning}
\include{ch09-conclusion}
\include{ch10-proposed}

{\small
\bibliographystyle{abbrv}
\bibliography{pr-refs}
}

\appendix
\chapter{Graph Search Proofs}
\label{appendix:gs-proofs}

This appendix presents some proofs relating the path-centric treatment
of graph search from Chapter~\ref{chap:inflate}
to traditional algorithms (e.g. A$^*$).

\begin{invariant}
The optimistically optimal path $path^* = A_s(G)$ can always be
segmented into
(a) a first sequence comprised of zero or more evaluated edges,
followed by
(b) a second sequence comprised of zero or more non-evaluated edges.
\label{inv:path-segmentation}
\end{invariant}

\begin{theorem}
Invariant~\ref{inv:path-segmentation} holds throughout the course of
$E_s$ [forward] (Algorithm~WHAT?).
\label{thm:seg-fwd}
\end{theorem}

\begin{proof}
At the first iteration, with no edges evaluated,
$path^*$ will contain only non-evaluated edges,
and the invariant trivially holds.

Consider the case where the invariant newly does not hold for $path^*$.
In this case, there exists at least one triple of adjacent vertices
on the path $v_a, v_b, v_c$
such that the edge $(v_a, v_b)$ is un-evaluated,
while the edge $(v_b, v_c)$ has been evaluated.
Due to our invariant,
there must have been some previous iteration which returned a
$path'^*$ which contained the triple
$v'_a, v_b, v_c$ for some other $v'_a$,
with $(v'_a, v_b)$ evaluated.
Therefore, the shortest distance to $v_b$ must known (and can be
reached through $v'_a$),
and any subsequent optimistic-optimal path through $v_b$
must consist of only evaluated segments until $v_b$
(due to the way $A_s$ breaks ties).
But our current $path^*$'s segment $(v_a, v_b)$ is un-evaluated!
This contradiction shows that the invariant must hold throughout the
algorithm.
\end{proof}

\end{document}
