%\documentclass{report}
\documentclass[nobib]{tufte-book}

\usepackage{standalone}

\usepackage{calc}

%\usepackage[bookmarks=true]{hyperref}

% symbols
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb} % for \square
% non-italicized math subscripts
\newcommand{\ms}[1]{\mbox{\scriptsize #1}}

% from http://tex.stackexchange.com/a/5255
\DeclareMathOperator*{\argmin}{arg\,min}

% algorithm stuff
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage{array}
\usepackage{graphicx}
%\usepackage{subcaption}
\usepackage[caption=false]{subfig} %[caption=false]
\usepackage{float} % for side-by-side figures?
% http://tex.stackexchange.com/a/95357

\usepackage{setspace}

\floatstyle{plain}
\newfloat{genericfloat}{t}{gflt}

\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,calc,patterns,positioning,shapes,decorations.pathmorphing}

% plots
\usepackage{pgfplots}

% pretty tables
\usepackage{multirow}
\usepackage{booktabs}

% custom title page
\usepackage{titling}

% for adjustwidth
\usepackage{changepage}

% include \paragraph as numbered
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{1} % 3

%\def\hidenotes{}
% list of commenters
\newcommand{\ssnote}[1]{{\xxnote{SS}{red}{#1}}}
\newcommand{\cdnote}[1]{{\xxnote{CD}{blue}{#1}}}
\newcommand{\mknote}[1]{{\xxnote{MK}{green}{#1}}}
% implement conditional notes (turn on/off with \hidenotes above)
\newcommand{\xxnote}[3]{}
\ifx\hidenotes\undefined
  \usepackage{color}
  \renewcommand{\xxnote}[3]{\color{#2}{#1: #3}}
\fi

% wide page for side by side figures, tables, etc
% see http://tex.stackexchange.com/a/154766
\newlength{\offsetpage}
\setlength{\offsetpage}{1.5in}
\newenvironment{widepage}
   {\begin{adjustwidth}{-\offsetpage}{-\offsetpage}%
    \addtolength{\textwidth}{2\offsetpage}}%
{\end{adjustwidth}}

% theorems
\newtheorem{invariant}{Invariant}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
% from http://www.maths.tcd.ie/~dwilkins/LaTeXPrimer/Theorems.html
\newenvironment{proof}[1][Proof]{\begin{trivlist}
   \item[\hskip \labelsep {\bfseries #1}]}{\hfill$\square$\end{trivlist}}

\title{Efficient Manipulation Task Planning via\\
   Reuse-Informed Optimization of Planning Effort}
\author{Christopher M. Dellin}
\date{\today}

\renewcommand{\maketitlehooka}{
\begin{fullwidth}
}

\renewcommand{\maketitlehookd}{
\begin{center}
\vspace{0.7in}
The Robotics Institute\\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\vspace{0.7in}
\textbf{Thesis Committee:}\\
Siddhartha Srinivasa, CMU RI (Chair)\\
Anthony Stentz, CMU RI\\
Maxim Likhachev, CMU RI\\
Lydia Kavraki, Rice University\\
%\vspace{0.7in}
%\emph{Submitted in partial fulfillment of the requirements\\
%for the degree of Doctor of Philosophy.}
\end{center}
\end{fullwidth}
}

\begin{document}

\maketitle

%\begin{abstract}
\begin{fullwidth}
\begin{adjustwidth}{1in}{1in}

{\LARGE \emph{Abstract}}

\vspace{0.2in}

In order to assist humans
with dangerous or menial tasks,
autonomous robots will need to
act under significant time and energy constraints.
At task time,
the amount of effort a robot spends planning directly
detracts from its total performance.
Manipulation tasks, however, present challenges
to efficient motion planning.
They are often tightly coupled --
while moving an object can be decomposed into
steps (reach, grasp, transfer, release),
each step requires choices (e.g. which grasp),
and committing to a bad choice
can render subsequent steps difficult;
this encourages longer planning horizons.
However,
an articulated robot
situated within a geometrically complex and dynamic environment
induces a high-dimensional configuration space
in which it is expensive to test for valid paths.
And since multi-step plans
require paths in changing valid subsets of configuration space,
it is difficult to reuse computation across steps
or maintain caches between tasks.

We focus on a motion planning approach for coupled multi-step
manipulation problems that is efficient over the entire task
(including both planning and execution).
We contend that the problem's cost structure
favors explicit handling of
both graph representation and task effort optimization,
and propose a graph search algorithm which captures these insights
given a model of planning effort.
We offer methods for roadmap construction
which seek to balance completeness with efficiency at task time.
We then unify previous work examining configuration space structure of
related problems (e.g. multi-step manipulation)
into a general set-theoretic formulation
which suggests a planning effort model
to be exploited by our roadmap search algorithm,
yielding a motion planner which
efficiently reuses computation between queries.
We also present a task planner
that maps a task decomposition into queries to our motion planner.
Our insights yield complementary components
which, taken together,
consitute an efficient approach to planning manipulation tasks.

This thesis proposes a heavy emphasis on experimental evaluation
of the individual constituent algorithms
and the approach as a whole.
We will compare against
state-of-the-art task and motion planners
on multiple robotic platforms,
in applications from home table clearing
to remote disaster response.
We also provide open-source implementations of our algorithms.

\end{adjustwidth}
\end{fullwidth}
%\end{abstract}

\tableofcontents

\include{ch01-intro}
\include{chxx-proposed-framework}
\include{ch11-proposed}

%{\small
%\bibliographystyle{abbrv}
%\bibliography{pr-refs}
%}

\bibliographystyle{abbrv}
\bibliography{pr-refs}
%\doccmddef{bibliography}

\end{document}
