
\begin{fullwidth}
\begin{adjustwidth}{1in}{1in}

\vphantom{.}

\vspace{0.2in}

{\LARGE \emph{Acknowledgements}}

\vspace{0.2in}

Thanks first and foremost to Sidd,
whose advice and guidance were indispensable for
this thesis
-- countless whiteboards replete with
vertices and edges, $\mathcal{C}$'s and queues,
each captured by a smartphone photo at the end of a meeting.
I was also exceedingly lucky to have such a distinguished
committee --
Tony, Max, and Lydia provided not only an extraordinary body of work
on which to build,
but also an array of helpful comments and suggestions which greatly
improved this dissertation.

\vspace{0.2cm}

Robotics research thrives on real hardware and real applications,
and my experiences on the CHIMP and ARM-S projects
at the NREC were pivotal to motivating and grounding my work.
Thanks especially to Tony, Drew Bagnell,
Clark Haynes, Mike Van de Weghe, Kyle Strabala, Jordan Brindza,
David Stager, Eric Meyhofer, Brian Zajac, Sean Hyde,
Jean-S\'{e}bastien Valois, Tom Galluzzo, Moslem Kazemi,
and everyone else who made those projects such a fun and rewarding
time for me.

\vspace{0.2cm}

I could not have asked for a better working environment
(or a bigger desk)
than what I found at the Personal Robotics Lab
-- but more importantly,
the people are motivated, amazingly smart, and always available
for a brainstorming session, technical discussion, code review,
practice talk, or free lunch.
Thanks especially to Mike Koval, Jen King, Aaron Johnson,
and Shushman Choudhury for your help and critical comments,
and to Clint, Gilwoo, Laura, Rachel, Pras, Pyry, Shervin, and Stefanos,
for being such great colleagues and friends.

\vspace{0.2cm}

I am eternally grateful to my parents,
who provided boundless love and support
-- and also very persistent encouragement
while this dissertation on lazy coloring was in the pipeline.
And to my fianc\'{e}e Anca,
I cannot imagine
a more compassionate critic,
a better friend,
or a more dedicated partner.
Thank you for giving me your enthusiastic support
and your insightful advice.
I certainly could not have finished without you!

\vspace{3.5cm} 

\noindent
This dissertation would not have been possible without funding from
National Science Foundation IIS (\#1409003),
Toyota Motor Engineering \& Manufacturing (TEMA),
and the Office of Naval Research.

\end{adjustwidth}
\end{fullwidth}
