\documentclass[nobib]{tufte-book}

\usepackage{standalone}

\usepackage{calc}

%\usepackage[bookmarks=true]{hyperref}
\usepackage{hyperref}

% symbols
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb} % for \square

% non-italicized math subscripts
\newcommand{\ms}[1]{\mbox{\scriptsize #1}}

% from http://tex.stackexchange.com/a/5255
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

% algorithm stuff
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage{array}
\usepackage{graphicx}

% the subcaption package is incompatible with tufte-book
% the caption package is incomatible with tufte-book
% the caption=false option to subfig prevents it from loading caption
\usepackage[caption=false]{subfig}
\usepackage{float} % for side-by-side figures?
% http://tex.stackexchange.com/a/95357

\usepackage{setspace}

\floatstyle{plain}
\newfloat{genericfloat}{h}{gflt}

\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,calc,patterns,positioning,shapes,decorations.pathmorphing}

% from http://tex.stackexchange.com/a/103691
% taken from manual
\makeatletter
\pgfdeclareshape{document}{
\inheritsavedanchors[from=rectangle] % this is nearly a rectangle
\inheritanchorborder[from=rectangle]
\inheritanchor[from=rectangle]{center}
\inheritanchor[from=rectangle]{north}
\inheritanchor[from=rectangle]{south}
\inheritanchor[from=rectangle]{west}
\inheritanchor[from=rectangle]{east}
% ... and possibly more
\backgroundpath{% this is new
% store lower right in xa/ya and upper right in xb/yb
\southwest \pgf@xa=\pgf@x \pgf@ya=\pgf@y
\northeast \pgf@xb=\pgf@x \pgf@yb=\pgf@y
% compute corner of ‘‘flipped page’’
\pgf@xc=\pgf@xb \advance\pgf@xc by-4pt % this should be a parameter
\pgf@yc=\pgf@yb \advance\pgf@yc by-4pt
% construct main path
\pgfpathmoveto{\pgfpoint{\pgf@xa}{\pgf@ya}}
\pgfpathlineto{\pgfpoint{\pgf@xa}{\pgf@yb}}
\pgfpathlineto{\pgfpoint{\pgf@xc}{\pgf@yb}}
\pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yc}}
\pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@ya}}
\pgfpathclose
% add little corner
\pgfpathmoveto{\pgfpoint{\pgf@xc}{\pgf@yb}}
\pgfpathlineto{\pgfpoint{\pgf@xc}{\pgf@yc}}
\pgfpathlineto{\pgfpoint{\pgf@xb}{\pgf@yc}}
\pgfpathlineto{\pgfpoint{\pgf@xc}{\pgf@yc}}
}
}
\makeatother

% pretty tables
\usepackage{multirow}
\usepackage{booktabs}

% see http://tex.stackexchange.com/a/19678
\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\refsub}[2]{\ref{#1}\subref{#1:#2}}

% custom title page
\usepackage{titling}

% for adjustwidth
\usepackage{changepage}

% include \paragraph as numbered
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{1} % 3

\usepackage{color}

%\def\hidenotes{}
% list of commenters
\newcommand{\cdnote}[1]{{\xxnote{CD}{blue}{#1}}}
\newcommand{\ssnote}[1]{{\xxnote{SS}{red}{#1}}}
\newcommand{\mknote}[1]{{\xxnote{MK}{green}{#1}}}
\newcommand{\scnote}[1]{{\xxnote{SC}{orange}{#1}}}
% implement conditional notes (turn on/off with \hidenotes above)
\newcommand{\xxnote}[3]{}
\ifx\hidenotes\undefined
  \renewcommand{\xxnote}[3]{\color{#2}{#1: #3}}
\fi

% wide page for side by side figures, tables, etc
% see http://tex.stackexchange.com/a/154766
\newlength{\offsetpage}
\setlength{\offsetpage}{1.5in}
\newenvironment{widepage}
   {\begin{adjustwidth}{-\offsetpage}{-\offsetpage}%
    \addtolength{\textwidth}{2\offsetpage}}%
{\end{adjustwidth}}

% theorems
\newtheorem{invariant}{Invariant}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
% from http://www.maths.tcd.ie/~dwilkins/LaTeXPrimer/Theorems.html
\newenvironment{proof}[1][Proof]{\begin{trivlist}
   \item[\hskip \labelsep {\bfseries #1}]}{\hfill$\square$\end{trivlist}}

% Efficient Manipulation Task Planning via
% Reuse-Informed Optimization of Planning Effort
\title{Completing Motion Tasks Efficiently in Complex Environments}
\author{Christopher M. Dellin}
\date{\today}
%\date{March 28, 2015}

\renewcommand{\maketitlehooka}{
\begin{fullwidth}
}

\renewcommand{\maketitlehookd}{
\begin{center}
\vspace{0.7in}
The Robotics Institute\\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\vspace{0.7in}
\textbf{Thesis Committee:}\\
Siddhartha Srinivasa, CMU RI (Chair)\\
Anthony Stentz, CMU RI\\
Maxim Likhachev, CMU RI\\
Lydia Kavraki, Rice University\\
%\vspace{0.7in}
%\emph{Submitted in partial fulfillment of the requirements\\
%for the degree of Doctor of Philosophy.}
\end{center}
\end{fullwidth}
}

\begin{document}

\maketitle

%\begin{abstract}
\begin{fullwidth}
\begin{adjustwidth}{1in}{1in}

{\LARGE \emph{Abstract}}

\vspace{0.2in}

\cdnote{I need to rewrite this -- while multi-step tasks
(e.g. arising from manipulation problems) are a well-suited application,
I think the thesis contributions are more broadly applicable.}

In order to assist humans
with dangerous or menial tasks,
autonomous robots will need to
act under significant time and energy constraints.
At task time,
the amount of effort a robot spends planning directly
detracts from its total performance.
Tasks such as manipulation, however, present challenges
to efficient motion planning.
They are often tightly coupled --
while moving an object can be decomposed into
steps (reach, grasp, transfer, release),
each step requires choices (e.g. which grasp),
and committing to a bad choice
can render subsequent steps difficult;
this encourages longer planning horizons.
However,
an articulated robot
situated within a geometrically complex and dynamic environment
induces a high-dimensional configuration space
in which it is expensive to test for valid paths.
And since multi-step plans
require paths in changing valid subsets of configuration space,
it is difficult to reuse computation across steps
or maintain caches between tasks.

We focus on a motion planning approach for coupled multi-step
manipulation problems that is efficient over the entire task
(including both planning and execution).
We contend that the problem's cost structure
favors explicit handling of
both graph representation and task effort optimization,
and propose a graph search algorithm which captures these insights
given a model of planning effort.
We offer methods for roadmap construction
which seek to balance completeness with efficiency at task time.
We then unify previous work examining configuration space structure of
related problems (e.g. multi-step manipulation)
into a general set-theoretic formulation
which suggests a planning effort model
to be exploited by our roadmap search algorithm,
yielding a motion planner which
efficiently reuses computation between queries.
We also present a task planner
that maps a task decomposition into queries to our motion planner.
Our insights yield complementary components
which, taken together,
constitute an efficient approach to planning manipulation tasks.

This dissertation places an emphasis on experimental evaluation
of the individual constituent algorithms
and the approach as a whole.
We will compare against
state-of-the-art task and motion planners
on multiple robotic platforms,
in applications from home table clearing
to remote disaster response.
We also provide open-source implementations of our algorithms.

\cdnote{Add acknowledgements!}

\end{adjustwidth}
\end{fullwidth}
%\end{abstract}

\tableofcontents

\chapter{Introduction}

\cdnote{I should pull a lot of the intro stuff from my proposal document.}

\cdnote{Add mega-outline-figure?}

Problem description.
Concise statement of objectives.

\noindent
Problem characterization.
What makes the problem difficult?
\begin{itemize}
\item Worlds are semi-structured (some things stay the same).
\item Collision checking is expensive.
\item Planning and execution cost are both important.
\item Must plan several steps ahead.
\item Words are dynamic (plans must be updated).
\end{itemize}

Focus on evaluation on real-world problems,
not contrived examples or asymptotic complexity.

\section{Outline of Approach}

Here is a broad outline of the thesis document.

\paragraph{Roadmap Methods for Motion Planning
   (Chapter~\ref{chap:roadmaps})}
Summarize the motion planning problem (C-space, etc).
We focus on roadmap methods.
Discuss recent results in assymptotic optimality.
Amenable to caching and parallelization.
\cdnote{This chapter is mostly about summarizing prior work.}

\paragraph{Fast Pathfinding on Graphs via Lazy Evaluation
   (Chapter~\ref{chap:lazysp})}
Challenge: validity checking on a roadmap is expensive.
Suppose we commit to a graph -- how should we search it?
We discuss the Lazy Shortest Path (LazySP)
algorithm.
Briefly discuss edge selectors.
Build on ideas such as D* and the Lazy PRM.
\cdnote{This is mostly from the ICAPS paper.}

\paragraph{Efficient Incremental Search
   (Chapter~\ref{chap:ibid})}
We need to search our roadmaps efficiently,
especially for lazy algorithms where there are small changes
between searches.
Introduce incremental bidirectional search (IBID)..
This is important because lazy approaches decouple the search
from the evaluation.

\paragraph{Maximizing Utility in Motion Planning
   (Chapter~\ref{chap:utility})}
Get back to the planning vs execution cost tradeoff.
How can a planner reason about this?
\cdnote{This is mostly from the LEMUR RSS paper.}

\paragraph{Planning over Configuration Space Families
   (Chapter~\ref{chap:family})}
Steps are incongruent.
Partial evaluation.
Optimistic family graphs.
Propositional logic.

\section{Review of Experimental Platforms}

Throughout, we will run experiments on three experimental platforms:
HERB, CHIMP, and IRB4400.

\include{thesis-ch02-roadmaps}

\include{thesis-ch03-lazysp}

\include{thesis-ch04-ibid}

\include{thesis-ch05-lemur}

\include{thesis-ch06-family}

\appendix

\chapter{Appendix: LazySP Proofs}
\label{sec:appendix-proofs}

\subsection{LazySP}

\begin{proof}[Proof of Theorem \ref{thm:lazy-optimality}]
Let $p^*$ be an optimal path w.r.t. $w$,
with $\ell^* = \mbox{len}(p^*, w)$.
Since $w_{\ms{est}}(e) \leq \epsilon \, w(e)$ and $\epsilon \geq 1$,
it follows that regardless of which edges are stored in $W_{\ms{eval}}$,
$w_{\ms{lazy}}(e) \leq \epsilon \, w(e)$,
and therefore
$\mbox{len}(p^*, w_{\ms{lazy}}) \leq \epsilon \, \ell^*$.
Now,
since the inner \textsc{ShortestPath} algorithm terminated with
$p_{\ms{ret}}$,
we know that
$\mbox{len}(p_{\ms{ret}}, w_{\ms{lazy}}) \leq \mbox{len}(p^*, w_{\ms{lazy}})$.
Further,
since the algorithm terminated with $p_{\ms{ret}}$,
each edge on $p_{\ms{ret}}$ has been evaluated;
therefore,
$\mbox{len}(p_{\ms{ret}}, w) = \mbox{len}(p_{\ms{ret}}, w_{\ms{lazy}})$.
Therefore,
$\mbox{len}(p_{\ms{ret}}, w) \leq \epsilon \, \ell^*$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:lazy-completeness}]
In this case,
the algorithm will evaluate at least unevaluated edge at
each iteration.
Since there are a finite number of edges,
eventually the algorithm will terminate.
\end{proof}

\subsection{A* Equivalence}

\begin{proof}[Proof of Invariant \ref{inv:astar-cundisc-popen}]
If $v$ is discovered, then it must either be on OPEN or CLOSED.
$v$ can be on CLOSED only after it has been expanded,
in which case $s$ would be discovered (which it is not).
Therefore, $v$ must be on OPEN.
\end{proof}

\begin{proof}[Proof of Invariant \ref{inv:astar-wless-popen}]
Clearly the invariant holds at the beginning of the algorithm,
with only $v_{\ms{start}}$ on OPEN.
If the invariant were to no longer hold after some iteration,
then there must exist some pair of discovered vertices $v$ and $v'$
with $v$ on CLOSED and $g[v] + w(v,v') < g[v']$.
Since $v$ is on CLOSED,
it must have been expanded at some previous iteration,
immediately after which the inequality could not have held
because $g[v']$ is updated upon expansion of $v$.
Therefore,
the inequality must have newly held after some intervening iteration,
with $v$ remaining on CLOSED.
Since the values $g$ are monotonically non-increasing and $w$ is fixed,
this implies that $g[v]$ must have been updated (lower).
However,
if this had happened,
then $v$ would have been removed from CLOSED and placed on OPEN.
This contradiction implies that the invariant holds at every iteration.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:astar-equiv-from-lazy}]
Consider path $p^*_{\ms{lazy}}$ with length $\ell^*_{\ms{lazy}}$
yielding frontier vertex $v_{\ms{frontier}}$ via \textsc{SelectExpand}.
Construct a vertex sequence $s$ as follows.
Initialize $s$ with the vertices on $p^*_{\ms{lazy}}$
from $v_{\ms{start}}$ to $v_{\ms{frontier}}$, inclusive.
Let $N$ be the number of consecutive vertices at the start of $s$
for which $f(v) = \ell^*_{\ms{lazy}}$
(Note that the first vertex on $p^*_{\ms{lazy}}$, $v_{\ms{start}}$,
must have $f(v_{\ms{start}}) = \ell^*_{\ms{lazy}}$,
so $N \geq 1$.)
Remove from the start of $s$ the first $N-1$ vertices.
Note that at most the first vertex on $s$ has
$f(v) = \ell^*_{\ms{lazy}}$,
and the last vertex on $s$ must be $v_{\ms{frontier}}$.

Now we show that each vertex in this sequence $s$,
considered by A* in turn,
exists on OPEN with minimal $f$-value.
Iteratively consider the following procedure for sequence $s$.
Throughout,
we know that there must not be any vertex with
$f(v) < \ell^*_{\ms{lazy}}$,
that would imply that a different path through $v_b$ shorter than
$\ell^*_{\ms{lazy}}$ exists,
in which case $p^*_{\ms{lazy}}$ could not have been chosen.

If the sequence has length $>1$,
then consider the first two vertices on $s$, $v_a$ and $v_b$.
By construction,
$f(v_a) = \ell^*_{\ms{lazy}}$
and 
$f(v_b) \neq \ell^*_{\ms{lazy}}$.
In fact, from above
we know that $f(v_b) > \ell^*_{\ms{lazy}}$.
Therefore,
we have that $f(v_a) < f(v_b)$,
therefore and $g[v_a] + w(v_a,v_b) < g[v_b]$.
By Invariant~\ref{inv:astar-wless-popen},
$v_a$ must be on OPEN,
and with $f(v_a) = \ell^*_{\ms{lazy}}$,
it can therefore be considered by A*.
After it is expanded,
$f(v_b) = \ell^*_{\ms{lazy}}$,
and we can repeat the above procedure
with the sequence formed by removing the $v_a$ from $s$.

If instead the sequence has length $1$,
then it must be exactly $(v_{\ms{frontier}})$,
with $f(v_{\ms{frontier}}) = \ell^*_{\ms{lazy}}$.
Since the edge after $f(v_{\ms{frontier}})$ is not
evaluated,
then by Invariant~\ref{inv:astar-cundisc-popen},
$v_{\ms{frontier}}$ must be on OPEN,
and will therefore be expanded next.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:astar-equiv-to-lazy}]
Given that all vertices in $s_{\ms{candidate}}$ besides the last
are re-expansions,
they can be expanded with no edge evaluations.
Once the last vertex,
$v_{\ms{frontier}}$,
is to be expanded by A*,
suppose it has $f$-value $\ell$.

First,
we will show that there exists a path with length $\ell$ w.r.t.
$w_{\ms{lazy}}$
wherein all edges before $v_{\ms{frontier}}$ have been evaluated,
and the first edge after $v_{\ms{frontier}}$ has not.
Let $p_a$ be a shortest path from $v_{\ms{start}}$
to $v_{\ms{frontier}}$ consisting of only evaluated edges.
The length of this $p_a$ must be equal to $g[v_{\ms{frontier}}]$;
if it were not,
there would be some previous vertex on $p_a$ with lower $f$-value
than $v_{\ms{frontier}}$,
which would necessarily have been expanded first.
Let $p_b$ be the a shortest path from $v_{\ms{frontier}}$
to $v_{\ms{goal}}$.
The length of $p_b$ must be $h_{\ms{lazy}}(v_{\ms{frontier}})$
by definition.
Therefore, the path $(p_a, p_b)$ must have length $\ell$,
and since $v_{\ms{frontier}}$ is a new expansion,
the first edge on $p_b$ must be unevaluated.

Second,
we will show that there does not exist any path shorter than $\ell$
w.r.t. $w_{\ms{lazy}}$.
Suppose $p'$ were such a path, with length $\ell' < \ell$.
Clearly, $v_{\ms{start}}$ would have $f$-value $\ell'$ (although
it may not be on OPEN).
Consider each pair of vertices $(v_a, v_b)$ along $p'$ in turn.
In each case,
if $v_b$ were either undiscovered,
or if $g[v_a] + w(v_a, v_b) < g[v_b]$,
then $v_a$ would be on OPEN
(via Invariants \ref{thm:lazy-completeness}
and \ref{inv:astar-wless-popen}, respectively)
with $f(v_a) = \ell'$,
and would therefore have been expanded before $v_{\ms{frontier}}$.
Otherwise,
we know that $f(v_b) = \ell'$,
and we can continue to the next pair on $p'$.
\end{proof}

\subsection{LWA* Equivalence}

\begin{proof}[Proof of Invariant \ref{inv:lwastar}]
Clearly the invariant holds at the beginning of the algorithm
with only $g[v_{\ms{start}}] = 0$,
since the inequality holds only for the out-edges of $v_{\ms{start}}$,
with $v_{\ms{start}}$ on $Q_v$.
Consider each subsequent iteration.
If a vertex $v$ is popped from $Q_v$,
then this may invalidate the invariant for all successors of $v$;
however,
since all out-edges are immediately added to $Q_e$,
the invariant must hold.
Consider instead if an edge $(v, v')$ which satisfies the inequality
is popped from $Q_e$.
Due to the inequality,
we know that $g[v']$ will be recalculated as
$g[v'] = g[v] + w(v,v')$,
so that the inequality is no longer satisfied for edge $(v,v')$.
However,
reducing the value $g[v']$ may introduce satisfied inequalities across
subsequent out-edges of $v'$,
but since $v'$ is added to $Q_v$,
the invariant continues to hold.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:lwastar-equiv-from-lazy}]
In the first component of the equivalence,
we will show that for any path $p$ minimizing $w_{\ms{lazy}}$
allowable to LazySP-Forward,
with $(v_a, v_b)$ the first unevaluated edge on $p$,
there exists a sequence of vertices and edges on
$Q_v$ and $Q_e$ allowable to LWA*
such that edge $(v_a, v_b)$ is the first to be newly evaluated.
Let the length of $p$ w.r.t. $w_{\ms{lazy}}$ be $\ell$.'

We will first show that no vertex on $Q_v$ or edge on $Q_e$
can have $f(\cdot) < \ell$.
Suppose such a vertex $v$, or edge $e$ with source vertex $v$,
exists.
Then $g[v] + h(v) < \ell$,
and there must be some path $p'$ consisting of an evaluated segment
from $v_{\ms{start}}$ to $v$ of length $g[v]$,
followed a segment from $v$ to $v_{\ms{goal}}$ of length $h(v)$.
But then this path should have been chosen by LazySP.

Next, we will show a procedure for generating an allowable
sequence for LWA*.
We will iteratively consider a sequence of path segments,
starting with the segment from $v_{\ms{start}}$ to $v_a$,
and becoming progressively shorter at each iteration by removing the
first vertex and edge on the path.
We will show that the first vertex on each segment $v_f$
has $g[v_f] = \ell - h(v_f)$.
By definition,
this is true of the first such segment, since $g[v_{\ms{start}}] = 0$.
For each but the last such segment,
consider the first edge, $(v_f, v_s)$.
If $v_s$ has the correct $g[\cdot]$,
we can continue to the next segment immediately.
Otherwise,
either $v_f$ is on $Q_v$ or $(v_f, v_s)$ is on $Q_e$ by
Invariant~\ref{inv:lwastar}.
If the former is true,
then $v_f$ can be popped from $Q_v$ with $f = \ell$,
thereby adding $(v_f, v_s)$ to $Q_e$.
Then,
$(v_f, v_s)$ can be popped from $Q_e$ with $f = \ell$,
resulting in $g[v_s] = \ell - h(v_s)$.
We can then move on to the next segment.

At the end of this process,
we have the trivial segment $(v_a)$,
with $g[v_a] = \ell - h(v_a)$.
If $v_a$ is on $Q_v$, then pop it (with $f(v_a) = \ell$),
placing $e_{ab}$ on $Q_e$;
otherwise, since $e_{ab}$ is unevaluated,
it must already be on $Q_e$.
Since $f(e_{ab}) = \ell$, we can pop and evaluate it.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:lwastar-equiv-to-lazy}]
Given that all vertices in $s_{\ms{candidate}}$ entail no edge evaluations,
and all edges therein are re-expansions,
they can be considered with no edge evaluations.
Once the last edge $e_{xy}$ is to be expanded by LWA*,
suppose it has $f$-value $\ell$.

First,
we will show that there exists a path with length $\ell$ w.r.t.
$w_{\ms{lazy}}$
which traverses unevaluated edge $e_{xy}$
wherein all edges before $v_x$ have been evaluated.
Let $p_x$ be a shortest path segment from $v_{\ms{start}}$
to $v_x$ consisting of only evaluated edges.
The length of $p_x$ must be equal to $g[v_x]$;
if it were not,
there would be some previous vertex on $p_x$ with lower $f$-value
than $v_x$,
which would necessarily have been expanded first.
Let $p_y$ be the a shortest path from $v_y$
to $v_{\ms{goal}}$.
The length of $p_y$ must be $h_{\ms{lazy}}(v_y)$
by definition.
Therefore, the path $(p_x, e_{xy}, p_y)$ must have length $\ell$.

Second,
we will show that there does not exist any path shorter than $\ell$
w.r.t. $w_{\ms{lazy}}$.
Suppose $p'$ were such a path, with length $\ell' < \ell$,
and with first unevaluated edge $e'_{xy}$.
Clearly, $v_{\ms{start}}$ has
$g[v_{\ms{start}}] = \ell' - h(v_{\ms{start}})$.
Consider each evaluated edge $e'_{ab}$ along $p'$ in turn.
In each case,
if $g[v'_b] \neq \ell' - h(v'_b)$,
then either $v'_a$ or $e'_{ab}$ would be on $Q_v$ or $Q_e$
with $f(\cdot) = \ell'$,
and would therefore be expanded before $e_{xy}$.
Therefore,
$e'_{xy}$ would then be popped from $Q_e$ with $f(e'_{xy}) = \ell'$,
and it would have been evaluated before $e_{xy}$ with $f(e_{xy}) = \ell$.
\end{proof}

\chapter{Appendix: LazySP Timing Results}
\label{sec:appendix-timing}

We include an accounting of the cumulative computation time taken by
each component of LazySP for each of the seven selectors
for each problem class (Figure~\ref{fig:table-timing-results}).

\begin{figure*}
   \begin{widepage}
   \centering
   {\small%
   \setlength{\tabcolsep}{0.06cm}%
   \begin{tabular}{l@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r@{\hskip 9pt}rc@{\hskip 0pt}r}
      \toprule
         & \multicolumn{3}{c}{Expand} & \multicolumn{3}{c}{Forward} & \multicolumn{3}{c}{Reverse} & \multicolumn{3}{c}{Alternate}
         & \multicolumn{3}{c}{Bisect} & \multicolumn{3}{c}{WeightSamp} & \multicolumn{3}{c}{Partition} \\
      \midrule
      \addlinespace[0.5em]
      PartConn & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (ms)}    &\bf1.22 &$\pm$&   0.04 &    1.96 &$\pm$&  0.06 &    1.86 &$\pm$&  0.06 &\bf1.20 &$\pm$& 0.03 &  2.41 &$\pm$& 0.06 & 4807.19 &$\pm$& 135.22 &   15.81 &$\pm$&  0.16 \\
      \;\;\emph{sel-init (ms)} & --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &   12.49 &$\pm$&  0.11 \\
      \;\;\emph{online (ms)}   &\bf1.22 &$\pm$&   0.04 &    1.96 &$\pm$&  0.06 &    1.86 &$\pm$&  0.06 &\bf1.20 &$\pm$& 0.03 &  2.41 &$\pm$& 0.06 & 4807.19 &$\pm$& 135.22 &    3.32 &$\pm$&  0.10 \\
      \;\;\emph{search (ms)}   &   0.48 &$\pm$&   0.01 &    1.12 &$\pm$&  0.03 &    1.05 &$\pm$&  0.03 &   0.68 &$\pm$& 0.02 &  1.38 &$\pm$& 0.04 &    0.70 &$\pm$&   0.02 &    0.68 &$\pm$&  0.02 \\
      \;\;\emph{sel (ms)}      &   0.02 &$\pm$&   0.00 &    0.01 &$\pm$&  0.00 &    0.01 &$\pm$&  0.00 &   0.01 &$\pm$& 0.00 &  0.03 &$\pm$& 0.00 & 4805.64 &$\pm$& 135.18 &    2.07 &$\pm$&  0.06 \\
      \;\;\emph{eval (ms)}     & --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  --\;\; &     &       \\
      \;\;\emph{eval (edges)}  &  87.10 &$\pm$&   2.39 &   35.86 &$\pm$&  1.04 &   34.84 &$\pm$&  1.04 &  22.23 &$\pm$& 0.60 & 44.81 &$\pm$& 1.11 &\bf20.66 &$\pm$&   0.57 &\bf20.39 &$\pm$&  0.56 \\
      \addlinespace[0.5em]
      UnitSquare & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (ms)}    &\bf0.91 &$\pm$&   0.03 &    1.47 &$\pm$&  0.06 &    1.49 &$\pm$&  0.06 &\bf0.94 &$\pm$& 0.03 &  1.71 &$\pm$& 0.04 & 3864.95 &$\pm$& 117.66 &   15.13 &$\pm$&  0.14 \\
      \;\;\emph{sel-init (ms)} & --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &   13.41 &$\pm$&  0.12 \\
      \;\;\emph{online (ms)}   &\bf0.91 &$\pm$&   0.03 &    1.47 &$\pm$&  0.06 &    1.49 &$\pm$&  0.06 &\bf0.94 &$\pm$& 0.03 &  1.71 &$\pm$& 0.04 & 3864.95 &$\pm$& 117.66 &    1.72 &$\pm$&  0.06 \\
      \;\;\emph{search (ms)}   &   0.35 &$\pm$&   0.01 &    0.79 &$\pm$&  0.03 &    0.82 &$\pm$&  0.03 &   0.51 &$\pm$& 0.02 &  0.92 &$\pm$& 0.02 &    0.75 &$\pm$&   0.02 &    0.45 &$\pm$&  0.01 \\
      \;\;\emph{sel (ms)}      &   0.01 &$\pm$&   0.00 &    0.01 &$\pm$&  0.00 &    0.01 &$\pm$&  0.00 &   0.01 &$\pm$& 0.00 &  0.02 &$\pm$& 0.00 & 3863.49 &$\pm$& 117.62 &    0.87 &$\pm$&  0.03 \\
      \;\;\emph{eval (ms)}     & --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  --\;\; &     &       \\
      \;\;\emph{eval (edges)}  &  69.21 &$\pm$&   2.55 &   27.29 &$\pm$&  1.03 &   27.69 &$\pm$&  1.02 &  17.82 &$\pm$& 0.60 & 32.62 &$\pm$& 0.72 &   15.58 &$\pm$&   0.47 &\bf14.08 &$\pm$&  0.46 \\
      \addlinespace[0.5em]
      ArmPlan (avg) & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (s)}    &  269.82 &$\pm$&  17.95 &\bf 5.90 &$\pm$&  0.46 &    8.22 &$\pm$&  0.53 &\bf5.96 &$\pm$& 0.31 &  7.34 &$\pm$& 0.43 & 3402.21 &$\pm$& 172.20 &  496.57 &$\pm$&  5.53 \\
      \;\;\emph{sel-init (s)} &  --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  490.77 &$\pm$&  5.51 \\
      \;\;\emph{online (s)}   &  269.82 &$\pm$&  17.95 &\bf 5.90 &$\pm$&  0.46 &    8.22 &$\pm$&  0.53 &\bf5.96 &$\pm$& 0.31 &  7.34 &$\pm$& 0.43 & 3402.21 &$\pm$& 172.20 &\bf 5.80 &$\pm$&  0.28 \\
      \;\;\emph{search (s)}   &    0.02 &$\pm$&   0.00 &    0.02 &$\pm$&  0.00 &    0.02 &$\pm$&  0.00 &   0.02 &$\pm$& 0.00 &  0.02 &$\pm$& 0.00 &    0.02 &$\pm$&   0.00 &    0.04 &$\pm$&  0.00 \\
      \;\;\emph{sel (s)}      &    0.00 &$\pm$&   0.00 &    0.00 &$\pm$&  0.00 &    0.00 &$\pm$&  0.00 &   0.00 &$\pm$& 0.00 &  0.00 &$\pm$& 0.00 & 3392.76 &$\pm$& 171.74 &    1.54 &$\pm$&  0.09 \\
      \;\;\emph{eval (s)}     &  269.78 &$\pm$&  17.95 &    5.87 &$\pm$&  0.45 &    8.20 &$\pm$&  0.52 &   5.94 &$\pm$& 0.31 &  7.31 &$\pm$& 0.43 &    9.39 &$\pm$&   0.57 &    4.21 &$\pm$&  0.22 \\
      \;\;\emph{eval (edges)} &  949.05 &$\pm$&  63.46 &   63.62 &$\pm$&  4.15 &   74.94 &$\pm$&  5.07 &  55.48 &$\pm$& 2.95 & 68.01 &$\pm$& 3.86 &   56.93 &$\pm$&   3.37 &\bf48.07 &$\pm$&  2.44 \\
      \addlinespace[0.25em]
      ArmPlan1 & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (s)}    &  109.09 &$\pm$&  14.15 &\bf 4.81 &$\pm$&  0.49 &   14.81 &$\pm$&  1.45 &   7.03 &$\pm$& 0.63 &  7.91 &$\pm$& 0.70 & 3375.35 &$\pm$& 319.81 &  496.74 &$\pm$&  8.22 \\
      \;\;\emph{sel-init (s)} &  --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  489.49 &$\pm$&  8.18 \\
      \;\;\emph{online (s)}   &  109.09 &$\pm$&  14.15 &\bf 4.81 &$\pm$&  0.49 &   14.81 &$\pm$&  1.45 &   7.03 &$\pm$& 0.63 &  7.91 &$\pm$& 0.70 & 3375.35 &$\pm$& 319.81 &    7.25 &$\pm$&  0.66 \\
      \;\;\emph{search (s)}   &    0.02 &$\pm$&   0.00 &    0.02 &$\pm$&  0.00 &    0.03 &$\pm$&  0.00 &   0.02 &$\pm$& 0.00 &  0.02 &$\pm$& 0.00 &    0.02 &$\pm$&   0.00 &    0.04 &$\pm$&  0.00 \\
      \;\;\emph{sel (s)}      &    0.00 &$\pm$&   0.00 &    0.00 &$\pm$&  0.00 &    0.00 &$\pm$&  0.00 &   0.00 &$\pm$& 0.00 &  0.00 &$\pm$& 0.00 & 3358.82 &$\pm$& 318.17 &    1.61 &$\pm$&  0.16 \\
      \;\;\emph{eval (s)}     &  109.07 &$\pm$&  14.15 &    4.78 &$\pm$&  0.49 &   14.77 &$\pm$&  1.44 &   7.01 &$\pm$& 0.63 &  7.88 &$\pm$& 0.70 &   16.47 &$\pm$&   1.68 &    5.59 &$\pm$&  0.51 \\
      \;\;\emph{eval (edges)} &  344.74 &$\pm$&  39.63 &\bf49.72 &$\pm$&  4.25 &   95.58 &$\pm$&  9.67 &  59.44 &$\pm$& 5.06 & 58.90 &$\pm$& 4.74 &   73.72 &$\pm$&   7.63 &\bf50.66 &$\pm$&  4.43 \\
      \addlinespace[0.25em]
      ArmPlan2 & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (s)}    &  166.19 &$\pm$&   9.29 &\bf 3.27 &$\pm$&  0.25 &    7.36 &$\pm$&  0.69 &   5.95 &$\pm$& 0.52 &  5.63 &$\pm$& 0.45 & 4758.04 &$\pm$& 407.56 &  495.21 &$\pm$& 12.65 \\
      \;\;\emph{sel-init (s)} &  -    - &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  489.22 &$\pm$& 12.64 \\
      \;\;\emph{online (s)}   &  166.19 &$\pm$&   9.29 &\bf 3.27 &$\pm$&  0.25 &    7.36 &$\pm$&  0.69 &   5.95 &$\pm$& 0.52 &  5.63 &$\pm$& 0.45 & 4758.04 &$\pm$& 407.56 &    5.99 &$\pm$&  0.48 \\
      \;\;\emph{search (s)}   &    0.01 &$\pm$&   0.00 &    0.01 &$\pm$&  0.00 &    0.02 &$\pm$&  0.00 &   0.01 &$\pm$& 0.00 &  0.01 &$\pm$& 0.00 &    0.02 &$\pm$&   0.00 &    0.03 &$\pm$&  0.00 \\
      \;\;\emph{sel (s)}      &    0.00 &$\pm$&   0.00 &    0.00 &$\pm$&  0.00 &    0.00 &$\pm$&  0.00 &   0.00 &$\pm$& 0.00 &  0.00 &$\pm$& 0.00 & 4750.16 &$\pm$& 406.98 &    2.03 &$\pm$&  0.22 \\
      \;\;\emph{eval (s)}     &  166.17 &$\pm$&   9.28 &\bf 3.26 &$\pm$&  0.25 &    7.34 &$\pm$&  0.69 &   5.93 &$\pm$& 0.52 &  5.61 &$\pm$& 0.45 &    7.82 &$\pm$&   0.61 &    3.91 &$\pm$&  0.27 \\
      \;\;\emph{eval (edges)} &  657.02 &$\pm$&  29.24 &\bf62.24 &$\pm$&  6.12 &   98.54 &$\pm$& 10.89 &  69.96 &$\pm$& 6.98 & 75.88 &$\pm$& 7.47 &\bf66.24 &$\pm$&   6.36 &\bf62.16 &$\pm$&  6.10 \\
      \addlinespace[0.25em]
      ArmPlan3 & & & & & & & & & & & & & & & & & & & & & \\
      \;\;\emph{total (s)}    &  534.16 &$\pm$&  55.64 &    9.61 &$\pm$&  1.33 &\bf 2.50 &$\pm$&  0.23 &   4.91 &$\pm$& 0.56 &  8.47 &$\pm$& 0.99 & 2073.23 &$\pm$& 198.75 &  497.76 &$\pm$& 10.27 \\
      \;\;\emph{sel-init (s)} &  --\;\; &     &        &  --\;\; &     &       &  --\;\; &     &       & --\;\; &     &      &--\;\; &     &      &  --\;\; &     &        &  493.59 &$\pm$& 10.21 \\
      \;\;\emph{online (s)}   &  534.16 &$\pm$&  55.64 &    9.61 &$\pm$&  1.33 &\bf 2.50 &$\pm$&  0.23 &   4.91 &$\pm$& 0.56 &  8.47 &$\pm$& 0.99 & 2073.23 &$\pm$& 198.75 &    4.17 &$\pm$&  0.43 \\
      \;\;\emph{search (s)}   &    0.02 &$\pm$&   0.01 &    0.02 &$\pm$&  0.00 &    0.02 &$\pm$&  0.00 &   0.02 &$\pm$& 0.00 &  0.02 &$\pm$& 0.00 &    0.03 &$\pm$&   0.01 &    0.04 &$\pm$&  0.00 \\
      \;\;\emph{sel (s)}      &    0.00 &$\pm$&   0.00 &    0.00 &$\pm$&  0.00 &    0.00 &$\pm$&  0.00 &   0.00 &$\pm$& 0.00 &  0.00 &$\pm$& 0.00 & 2069.29 &$\pm$& 198.53 &    0.98 &$\pm$&  0.13 \\
      \;\;\emph{eval (s)}     &  534.10 &$\pm$&  55.63 &    9.58 &$\pm$&  1.33 &    2.48 &$\pm$&  0.23 &   4.89 &$\pm$& 0.56 &  8.44 &$\pm$& 0.99 &    3.90 &$\pm$&   0.31 &    3.15 &$\pm$&  0.32 \\
      \;\;\emph{eval (edges)} & 1845.38 &$\pm$& 195.57 &   78.90 &$\pm$& 10.36 &\bf30.70 &$\pm$&  3.62 &  37.04 &$\pm$& 4.59 & 69.26 &$\pm$& 7.97 &\bf30.82 &$\pm$&   3.60 &\bf31.38 &$\pm$&  3.80 \\
      \addlinespace[0.25em]
      \bottomrule
   \end{tabular}%
   }%
   \end{widepage}
   \vspace{0.5cm}
   \caption{
      Detailed timing results for each selector.
      The actual edge weights for the illustrative
      PartConn and UnitSquare problems were pre-computed,
      and therefore their timings are not included.
      The Partition selector requires initialization of the $Z$-values
      (\ref{eqn:partitionfn}) for the graph using only the estimated
      edge weights.
      Since this is not particular to either the actual edge weights
      (e.g. from the obstacle distribution)
      or the start/goal vertices from a particular instance,
      this initialization (\emph{sel-init}) is considered separately.
      The online running time (\emph{online}) is broken into LazySP's
      three primary steps: the inner search (\emph{search}),
      invoking the edge selector (\emph{sel}),
      and evaluating edges (\emph{eval}).
      We also show the number of edges evaluated.}
   \label{fig:table-timing-results}
\end{figure*}




%\include{ch01-intro}
%\include{chxx-proposed-framework}
%\include{ch11-proposed}

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}
