\chapter{Appendix: Incrementally Calculating Partition Functions on Graphs}
\label{chap:appendix-partition}

\paragraph{Problem Definition.}
Consider a directed graph $G=(V,E)$ endowed with an edge weight
function $w : E \rightarrow \mathbb{R}$.
Between any two vertices $x,y \in V$,
there exist a (potentially infinite) set of paths $P_{xy}$,
\marginnote{Note that we do not restrict consideration
to only simple paths on $G$.}
with the length of any path given by
$\mbox{len} : P_{xy} \rightarrow \mathbb{R}$ as in
(\ref{eqn:lazysp:len-definition}).
Between each such pair of vertices $x,y$,
one can compute the \emph{partition function} denoted $Z_{xy}$,
defined as a sum over all possible paths as follows:
\begin{equation}
   Z_{xy} = \sum_{p_{xy} \in P_{xy}} \exp(- \beta \, \mbox{len}(p_{xy})),
   \label{eqn:def}
\end{equation}
with $\beta$ a fixed real-valued parameter
(commonly called an inverse temperature in statistical mechanics).
We wish to compute and maintain this partition function value
between all pairs of vertices $x$ and $y$ on $G$.

\paragraph{An Incremental Approach.}
We propose an incremental method for calculating $Z$ between all pairs
on a graph.
We will proceed by initializing the values $Z_{xy}$ for each pair
on a graph with no edges,
and then show how we can update these values as edges are added
or removed.

First,
consider the graph with no edges $G_0 = (V, \emptyset)$.
On this graph, there exists no paths between each pair of vertices
$x,y$ with $x \neq y$.
On the other hand,
for $x=y$ there exists exactly one path
containing no edges (and therefore with length $0$).
Thus, we can initialize our values $Z_{xy}$ with:
\begin{equation}
   Z_{xy} = \left\{ \begin{array}{cl}
      1 & \mbox{if } x = y, \\
      0 & \mbox{otherwise}.
   \end{array}\right.
\end{equation}

\paragraph{Adding Edges.}
We can next establish the inductive step.
Suppose we compare two directed graphs $G$ and $G'$,
where $V' = V$ and $E' = E \cup \{ e_{ab} \}$,
and with new edge $e_{ab} : a \rightarrow b$ having weight $w_{ab}$.
For arbitrary vertices $x$ and $y$, we can write $Z'_{xy}$ as follows:
\begin{equation}
   Z'_{xy} = S^{(0)} + S^{(1)} + S^{(2)} + \dots
   \label{eqn:sums}
\end{equation}
where $S^{(k)}$ is the sum from (\ref{eqn:def})
over only the subset of paths that traverse $e_{ab}$ exactly $k$ times.
We note immediately that $S^{(0)} = Z_{xy}$.

Next, we consider the sum $S^{(1)}$,
that is, the sum over all paths which use the new edge $e_{ab}$
exactly once.
We note that each path which contributes to this sum consists of
three segments:
(a) a path segment from $x$ to $a$,
followed by (b) the new edge $e_{ab}$,
followed by (c) a path segment from $b$ to $y$.
Since the sum in question consists exactly of the sum over all unique
paths which follow this template,
we see that we can write $S^{(1)}$ as follows:
\begin{equation}
   S^{(1)} = \sum_{p_{xa}} \sum_{p_{by}}
      \exp\left(
         - \beta \left[ \mbox{len}(p_{xa}) + w_{ab} + \mbox{len}(p_{by}) \right]
         \right)
\end{equation}
Note that both $p_{xa} \in P_{xa}$ and $p_{by} \in P_{by}$
are over all paths on the original graph $G$.
We can then rewrite this simply as:
\begin{equation}
   S^{(1)} = Z_{xa} \, \exp(-\beta \, w_{ab}) \, Z_{by}.
\end{equation}
We can likewise write $S^{(2)}$ as:
\begin{equation}
   S^{(2)} = Z_{xa} \, \exp(-\beta \, w_{ab}) \, Z_{ba} \, \exp(-\beta \,  w_{ab}) \, Z_{by}.
\end{equation}
That is,
this sum consists of paths which arrive from $x$ to $a$ through $G$,
traverse the edge $e_{ab}$ once,
then traverse the original $G$ in some way from $b$ back to $a$,
traverse the edge $e_{ab}$ a second time,
and then proceed from $b$ to $y$.
This decomposition allows us to rewrite
the entire sum from (\ref{eqn:sums}) as:
\begin{equation}
   Z'_{xy} = Z_{xy} + Z_{xa} \, \exp(-\beta \, w_{ab}) \, Z_{by}
      \sum_{k=0}^{\infty} \left[ Z_{ba} \, \exp(-\beta \, w_{ab}) \right]^k. 
\end{equation}
As this is a geometric series, it will converge as long as
$Z_{ba} < \exp(\beta \, w_{ab})$.
In this case,
we have:
\begin{equation}
   Z'_{xy} = Z_{xy} + \frac{Z_{xa} \, Z_{by}}{\exp(\beta \, w_{ab}) - Z_{ba}}.
   \label{eqn:partition:addition}
\end{equation}
\marginnote{Note that the addition of an undirected edge between
$a$ and $b$ must entail two successive applications of
(\ref{eqn:partition:addition}).}
This allows us to accommodate arbitrary edge additions while maintaining
the correct values $Z_{xy}$ over all pairs of vertices on $G$.

\paragraph{Removing Edges.}
We can establish a similar result in the case that an existing edge
is removed from the graph.
Consider the case that you have a graph $G'$,
with partition function values $Z'$ between all pairs of vertices.
You then remove some existing edge $e_{ab}$ with weight $w_{ab}$,
yielding new graph $G$.
What can we say about the new values $Z$?

We proceed by applying (\ref{eqn:partition:addition})
to the edge to be removed $e_{ab}$:
\begin{equation}
   Z'_{ba} - Z_{ba} - \frac{Z_{ba}^2}{\exp(\beta w_{ab}) - Z_{ba}} = 0
\end{equation}
\begin{equation}
   \left[\exp(\beta w_{ab}) - Z_{ba} \right] Z'_{ba} - \exp(\beta w_{ab}) Z_{ba} = 0
\end{equation}
\begin{equation}
   \left[ \exp(\beta w_{ab}) - Z_{ba} \right]
   \left[ \exp(\beta w_{ab}) + Z'_{ba} \right]
   = \exp(2 \beta w_{ab})
\end{equation}
\begin{equation}
   \exp(\beta w_{ab}) - Z_{ba}
   = \frac{\exp(2 \beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}}
   \label{eqn:zba-convert}
\end{equation}
We can then use (\ref{eqn:zba-convert}) to express
$Z_{xa}$ and $Z_{by}$ in terms of $Z'_{xa}$ and $Z'_{by}$,
respectively:
\begin{equation}
   Z_{xa} + \frac{Z_{xa} \, Z_{ba}}{\exp(\beta w_{ab}) - Z_{ba}} = Z'_{xa}
   \longrightarrow
   Z_{xa} = \frac{\exp(\beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}} Z'_{xa}
\end{equation}
\begin{equation}
   Z_{by} + \frac{Z_{ba} \, Z_{by}}{\exp(\beta w_{ab}) - Z_{ba}} = Z'_{by}
   \longrightarrow
   Z_{by} = \frac{\exp(\beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}} Z'_{by}
\end{equation}
Lastly, we can combine (\ref{eqn:partition:addition})
and (\ref{eqn:zba-convert}) to express the desired value $Z_{xy}$
only in terms of values on $G'$:
\begin{equation}
   Z_{xy} = Z'_{xy} -
   \frac{
   \left[ \frac{\exp(\beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}} Z'_{xa} \right]
   \,
   \left[ \frac{\exp(\beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}} Z'_{by} \right]
   }{
   \left[ \frac{\exp(2 \beta w_{ab})}{\exp(\beta w_{ab}) + Z'_{ba}} \right]
   }
\end{equation}
\begin{equation}
   Z_{xy} = Z'_{xy} -
   \frac{Z'_{xa} Z'_{by}}{\exp(\beta w_{ab}) + Z'_{ba}}
\end{equation}
This allows us to accommodate edge deletions.
